Online Appendix

### 2019-08-12 appendix/Online_appendix_2019.tex
Up to conclusion

>>>>

\section{Fixed wage graphs}
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_10fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_11fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_13fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_14fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_16fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_17fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_18fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_21fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_23fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_25fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_29fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_30fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_33fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_35fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_36fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_39fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_42fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_43fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_44fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_45fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_48fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_51fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_55fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_59fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_66fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_71fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_75fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_77fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_81fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_82fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_83fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_85fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_87fixratiov3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_88fixratiov3"}
\newline

\newpage
\section{Fixed wages}

\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_10"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_11"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_13"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_14"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_16"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_17"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_18"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_21"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_23"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_25"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_29"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_30"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_33"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_35"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_36"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_39"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_42"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_43"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_44"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_45"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_48"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_51"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_55"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_59"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_66"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_71"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_75"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_77"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_nowW_occ_81"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_82v3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_83v3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_85v3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_87v3"}
\newline
\includegraphics[width=.8\textwidth]{"/Users/Miriam/OneDrive/Box Sync/TYPlocal/output/graphs/Splot_occ_88v3"}
\newline
